```{r}
###Steph Bossert lab
### Lab 2
```

```{r}

library(tidyverse)
plastic_waste <- read_csv("data/plastic-waste.csv")
 View(plastic_waste) 

ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2)

plastic_waste %>%
  filter(plastic_waste_per_cap > 3.5)
```

#Plot, using histograms, the distribution of plastic waste per capita faceted by continent. What can you say about how the continents compare to each other in terms of their plastic waste per capita?
```{r}
ggplot(plastic_waste, aes(x = plastic_waste_per_cap, 
                  fill = entity)) +
  geom_histogram(binwidth = 0.2,
                 alpha = 0.5) +
  labs(
    x = "Plastic Per Capita",
    y = "Frequency",
    title = "Amounts of Plastic per Country per Capita"
  )
```

```{r}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_density()

ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density()  

ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.7)
```

#Recreate the density plots above using a different (lower) alpha level that works better for displaying the density curves for all continents.
```{r}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.2)
```

#Describe why we defined the color and fill of the curves by mapping aesthetics of the plot but we defined the alpha level as a characteristic of the plotting geom. 
Fill/color help us visualize the data (mapping aestheticis of the plot), alpha level is separate from the aesthetics and therefor adjust it when geom_density

#Convert your side-by-side box plots from the previous task to violin plots. What do the violin plots reveal that box plots do not? What features are apparent in the box plots but not in the violin plots?
The violin pllots shows a continuous distribution

```{r}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent,
                     y = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_violin(alpha = 0.2)
```

#Visualize the relationship between plastic waste per capita and mismanaged plastic waste per capita using a scatterplot. Describe the relationship.

```{r}
ggplot(plastic_waste, aes(x = plastic_waste_per_cap, y = mismanaged_plastic_waste_per_cap)) +
  geom_point()
```

#Color the points in the scatterplot by continent. Does there seem to be any clear distinctions between continents with respect to how plastic waste per capita and mismanaged plastic waste per capita are associated?
```{r}
ggplot(plastic_waste, aes(x = plastic_waste_per_cap, y = mismanaged_plastic_waste_per_cap, color = continent)) +
  geom_point()
```
#Visualize the relationship between plastic waste per capita and total population as well as plastic waste per capita and coastal population. You will need to make two separate plots. Do either of these pairs of variables appear to be more strongly linearly associated?
```{r}
  ggplot(plastic_waste, aes(x = plastic_waste_per_cap, y = total_pop, color = continent)) +
  geom_point()
ggplot(plastic_waste, aes(x = plastic_waste_per_cap, y = coastal_pop, color = continent)) +
  geom_point()
```
